\section{Rigorous Confidence Calculation}
\label{sec:confidence_math}

\subsection{Theoretical Foundation: Subjective Logic}
Standard Dempster-Shafer Theory \cite{shafer1976mathematical} assumes independent evidence. In HINs, we adopt \textbf{Subjective Logic} \cite{josang2016subjective} to represent evidence as an \textbf{Opinion} $\omega = (b, d, u, a)$, where $b$, $d$, and $u$ represent belief, disbelief, and uncertainty respectively, and $a$ is the base rate.

\subsection{Mathematical Improvements}

\subsubsection{Discounting Operator (Trust Decay)}
To model the decay of evidence strength through long graph paths, we use the \textbf{Discounting Operator} $\otimes$:
\begin{equation}
\omega_{D \to S} = \omega_{e_1} \otimes \omega_{e_2} \otimes \dots \otimes \omega_{s}
\end{equation}

\subsubsection{Consensus and Conflict Reallocation}
Standard Dempster normalization can lead to "Certainty Inflation" in conflicting graphs. We implement \textbf{Yager's Rule} re-defined for Subjective Logic. Instead of normalizing via $1-K$, the conflicting mass $K$ is re-allocated to \textbf{Uncertainty ($u$)}:
\begin{equation}
u_{fused} = \frac{u_1 u_2 + K}{1} = u_1 u_2 + K
\end{equation}
This ensure that disagreement between repositories (e.g., Repo A says "Expert", Repo B says "Novice") results in higher uncertainty rather than an arbitrary choice between the two.

\subsection{Path Dependency Modeling}
Using \textbf{Dirichlet Distributions}, we map opinions to probability density functions, allowing the system to handle the sparsity of interactions inherent in private or small-scale developer repositories.
\begin{itemize}
    \item \textbf{Belief (Bel):} Lower bound of confidence.
    \begin{equation}
    Bel(S) = \sum_{X \subseteq S} m(X) = m(\{S\})
    \end{equation}
    \item \textbf{Plausibility (Pl):} Upper bound of confidence.
    \begin{equation}
    Pl(S) = \sum_{X \cap S \neq \emptyset} m(X) = m(\{S\}) + m(\Theta)
    \end{equation}
\end{itemize}

\subsection{Application to Skill Inference}
The Confidence Score $C(s|d)$ is the \textbf{Belief} function result:
\begin{equation}
C(s|d) = Bel_{final}(\{Skill\})
\end{equation}
